\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 Limber_Comment.tex
Limber_Comment.tex: Addressed SJ's comments

\begin{abstract}
Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

This comment is structured as follows.  In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.  We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys. In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.

>>>>

\begin{abstract}
Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey}.

@@

This comment is structured as follows.  In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.  We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys. In section~\ref{sec:cfhtlens} we compare with \citet{kitching/etal:2016} our conclusions of a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013}.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact in our analysis of numerical simulations and CMB lensing.
